Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-02-24 awipev-CO2.Rmd
seafet calibration period 5 updated

The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu°C`.

@@

#put interval in a list with the start date of seaFET measurements
sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")

>>>>

The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu`°C.

@@

#put interval in a list with the start date of seaFET measurements
sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
#Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
